Supplementary Information: Quantifying the pathways to life using assembly spaces

### 2021-05-11 papers/assembly/I/main.tex
[papers] Add to the Petri net subsection

\tikzstyle{empty}=[circle,fill=none, draw=none]
\tikzstyle{inputdot}=[circle,fill=black,draw=black, scale=.5]
\tikzstyle{dot}=[circle,fill=black,draw=black]
\tikzstyle{bounding}=[circle,dashed, fill=none,draw=black, scale=9.00]
\tikzstyle{simple}=[-,draw=black,line width=1.000]
\tikzstyle{inarrow}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.000]
\tikzstyle{tick}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\draw (0,-0.1) -- (0,0.1);}},line width=1.000]
\tikzstyle{inputarrow}=[->,draw=black, shorten >=.05cm]
\tikzstyle{sitemap}=[->, dashed, draw=red, ultra thick, shorten >=.05cm]
\tikzstyle{transitionmap}=[->, dashed, draw=blue, ultra thick, shorten >=.05cm]

@@

@@

Consider, for example, the Petri $P$ net described by $S(P) = \{ A, B, C, AA, AB, AAAB \}$ and $T(P) = \{ \alpha, \beta, \gamma, \delta \}$ with source and target maps:

\begin{align*}
    \sigma(\alpha) &= 2A           & \tau(\alpha) &= AA         \\
    \sigma(\beta)  &= A + B        & \tau(\beta)  &= AB         \\
    \sigma(\gamma) &= AA + AB + C  & \tau(\gamma) &= AAAB + C   \\
    \sigma(\delta) &= AAAB         & \tau(\delta) &= A + AA + B.
\end{align*}

A natural way of graphically representing this $P$ is with a bipartite multigraph:

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (0, 0.8) {$A$};
            \node [style=site] (B) at (0, -0.8) {$B$};
            \node [style=site] (C) at (6, -1.6) {$C$};
            \node [style=site] (AA) at (4, 0.8) {$AA$};
            \node [style=site] (AB) at (4, -0.8) {$AB$};
            \node [style=site] (AAAB) at (8, 0) {$AAAB$};
            \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
            \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
            \node [style=transition] (tau3) at (6, 0) {$\gamma$};
            \node [style=transition] (tau4) at (10, 0) {$\delta$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, bend right=15] (A) to (tau1);
            \draw [style=inarrow, bend left=15] (A) to (tau1);
            \draw [style=inarrow, bend right=15] (A) to (tau2);
            \draw [style=inarrow] (tau1) to (AA);
            \draw [style=inarrow] (B) to (tau2);
            \draw [style=inarrow] (tau2) to (AB);
            \draw [style=inarrow] (AA) to (tau3);
            \draw [style=inarrow] (AB) to (tau3);
            \draw [style=inarrow, bend left=30] (C) to (tau3);
            \draw [style=inarrow] (tau3) to (AAAB);
            \draw [style=inarrow, bend left=30] (tau3) to (C);
            \draw [style=inarrow] (AAAB) to (tau4);
            \draw [style=inarrow, bend right=30] (tau4) to (A);
            \draw [style=inarrow, bend right=30] (tau4) to (AA);
            \draw [style=inarrow, bend left=40] (tau4) to (B);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

@@

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (0, 0.8) {$A$};
            \node [style=site] (B) at (0, -0.8) {$B$};
            \node [style=site] (C) at (6, -1.6) {$C$};
            \node [style=site] (AA) at (4, 0.8) {$AA$};
            \node [style=site] (AB) at (4, -0.8) {$AB$};
            \node [style=site] (AAAB) at (8, 0) {$AAAB$};
            \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
            \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
            \node [style=transition] (tau3) at (6, 0) {$\gamma$};
            \node [style=transition] (tau4) at (10, 0) {$\delta$};

@@

            \node [text=red, scale=2] (g) at (-1.5, -3) {$g$};
            \node [text=blue, scale=2] (f) at (0.5, -3) {$f$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau1);
            \draw [style=inarrow, draw=gray!80, bend left=15] (A) to (tau1);
            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau2);
            \draw [style=inarrow, draw=gray!80] (tau1) to (AA);
            \draw [style=inarrow, draw=gray!80] (B) to (tau2);
            \draw [style=inarrow, draw=gray!80] (tau2) to (AB);
            \draw [style=inarrow, draw=gray!80] (AA) to (tau3);
            \draw [style=inarrow, draw=gray!80] (AB) to (tau3);
            \draw [style=inarrow, draw=gray!80, bend left=30] (C) to (tau3);
            \draw [style=inarrow, draw=gray!80] (tau3) to (AAAB);
            \draw [style=inarrow, draw=gray!80, bend left=30] (tau3) to (C);
            \draw [style=inarrow, draw=gray!80] (AAAB) to (tau4);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau4) to (A);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau4) to (AA);
            \draw [style=inarrow, draw=gray!80, bend left=40] (tau4) to (B);

            \draw [style=inarrow, draw=gray!80, bend left=15] (W) to (tau5);
            \draw [style=inarrow, draw=gray!80, bend right=15] (W) to (tau5);
            \draw [style=inarrow, draw=gray!80, bend left=15] (tau5) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=15] (tau5) to (X);
            \draw [style=inarrow, draw=gray!80, bend left=15] (X) to (tau6);
            \draw [style=inarrow, draw=gray!80, bend right=15] (X) to (tau6);
            \draw [style=inarrow, draw=gray!80] (tau6) to (Y);
            \draw [style=inarrow, draw=gray!80, bend left=20] (Y) to (tau7);
            \draw [style=inarrow, draw=gray!80] (Y) to (tau7);
            \draw [style=inarrow, draw=gray!80, bend right=20] (Y) to (tau7);
            \draw [style=inarrow, draw=gray!80] (tau7) to (Z);
            \draw [style=inarrow, draw=gray!80, bend left=50] (tau7.south) to (Y.south);
            \draw [style=inarrow, draw=gray!80] (Z) to (tau8);
            \draw [style=inarrow, draw=gray!80, bend left=30] (tau8) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (Y);

            \draw [style=sitemap, bend right=30] (A) to (X);
            \draw [style=sitemap, bend right=30] (B) to (X);
            \draw [style=sitemap, bend right=30] (AA) to (Y);
            \draw [style=sitemap, bend right=30] (AB) to (Y);
            \draw [style=sitemap, bend right=30] (C) to (Y);
            \draw [style=sitemap, bend right=30] (AAAB) to (Z);
            \draw [style=transitionmap, bend right=30] (tau1) to (tau6);
            \draw [style=transitionmap, bend right=30] (tau2) to (tau6);
            \draw [style=transitionmap, bend right=30] (tau3) to (tau7);
            \draw [style=transitionmap, bend right=30] (tau4) to (tau8);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

@@

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (0, 0.8) {$A$};
            \node [style=site] (B) at (0, -0.8) {$B$};
            \node [style=site] (C) at (6, -1.6) {$C$};
            \node [style=site] (AA) at (4, 0.8) {$AA$};
            \node [style=site] (AB) at (4, -0.8) {$AB$};
            \node [style=site] (AAAB) at (8, 0) {$AAAB$};
            \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
            \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
            \node [style=transition] (tau3) at (6, 0) {$\gamma$};

            \node [style=site] (W) at (-4, -6) {$W$};
            \node [style=site, fill=green!20] (X) at (0, -6) {$X$};
            \node [style=site, fill=green!20] (Y) at (4, -6) {$Y$};
            \node [style=site, fill=green!20] (Z) at (8, -6) {$Z$};
            \node [style=transition] (tau5) at (-2, -6) {$\phi$};
            \node [style=transition, fill=yellow!20] (tau6) at (2, -6) {$\chi$};
            \node [style=transition, fill=yellow!20] (tau7) at (6, -6) {$\psi$};
            \node [style=transition] (tau8) at (10, -6) {$\omega$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau1);
            \draw [style=inarrow, draw=gray!80, bend left=15] (A) to (tau1);
            \draw [style=inarrow, draw=gray!80, bend right=15] (A) to (tau2);
            \draw [style=inarrow, draw=gray!80] (tau1) to (AA);
            \draw [style=inarrow, draw=gray!80] (B) to (tau2);
            \draw [style=inarrow, draw=gray!80] (tau2) to (AB);
            \draw [style=inarrow, draw=gray!80] (AA) to (tau3);
            \draw [style=inarrow, draw=gray!80] (AB) to (tau3);
            \draw [style=inarrow, draw=gray!80, bend left=30] (C) to (tau3);
            \draw [style=inarrow, draw=gray!80] (tau3) to (AAAB);
            \draw [style=inarrow, draw=gray!80, bend left=30] (tau3) to (C);

            \draw [style=inarrow, draw=gray!80, bend left=15] (W) to (tau5);
            \draw [style=inarrow, draw=gray!80, bend right=15] (W) to (tau5);
            \draw [style=inarrow, draw=gray!80, bend left=15] (tau5) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=15] (tau5) to (X);
            \draw [style=inarrow, draw=red, bend left=15] (X) to (tau6);
            \draw [style=inarrow, draw=red, bend right=15] (X) to (tau6);
            \draw [style=inarrow, draw=red] (tau6) to (Y);
            \draw [style=inarrow, draw=red, bend left=20] (Y) to (tau7);
            \draw [style=inarrow, draw=red] (Y) to (tau7);
            \draw [style=inarrow, draw=red, bend right=20] (Y) to (tau7);
            \draw [style=inarrow, draw=red] (tau7) to (Z);
            \draw [style=inarrow, draw=red, bend left=50] (tau7.south) to (Y.south);
            \draw [style=inarrow, draw=gray!80] (Z) to (tau8);
            \draw [style=inarrow, draw=gray!80, bend left=30] (tau8) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (X);
            \draw [style=inarrow, draw=gray!80, bend right=30] (tau8) to (Y);

            \draw [style=sitemap, bend right=30, shorten >=2mm] (A) to (X);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (B) to (X);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (AA) to (Y);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (AB) to (Y);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (C) to (Y);
            \draw [style=sitemap, bend right=30, shorten >=2mm] (AAAB) to (Z);
            \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau1) to (tau6);
            \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau2) to (tau6);
            \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau3) to (tau7);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

@@

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (2, 0.8) {$A$};
            \node [style=site] (B) at (2, -0.8) {$B$};
            \node [style=transition] (tau1) at (0, 0) {$\alpha$};
            \node [style=transition] (tau2) at (4, 0) {$\beta$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, bend left=15] (tau1) to (A);
            \draw [style=inarrow, bend right=15] (tau1) to (B);
            \draw [style=inarrow, bend left=15] (A) to (tau2);
            \draw [style=inarrow, bend right=15] (B) to (tau2);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

@@

\begin{figure}[!h]
    \scalebox{0.6}{
    \begin{tikzpicture}
        \begin{pgfonlayer}{nodelayer}
            \node [style=site] (A) at (0, 0.8) {$A$};
            \node [style=site] (B) at (0, -0.8) {$B$};
            \node [style=site] (C) at (6, -1.6) {$C$};
            \node [style=site] (AA) at (4, 0.8) {$AA$};
            \node [style=site] (AB) at (4, -0.8) {$AB$};
            \node [style=site] (AAAB) at (8, 0) {$AAAB$};
            \node [style=transition, fill=green!20] (tau1) at (2, 0.8) {$\alpha$};
            \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
            \node [style=transition, fill=green!20] (tau3) at (6, 0) {$\gamma$};
            \node [style=transition] (tau4) at (10, 0) {$\delta$};
        \end{pgfonlayer}
        \begin{pgfonlayer}{edgelayer}
            \draw [style=inarrow, bend right=15] (A) to (tau1);
            \draw [style=inarrow, bend left=15] (A) to (tau1);
            \draw [style=inarrow, bend right=15] (A) to (tau2);
            \draw [style=inarrow] (tau1) to (AA);
            \draw [style=inarrow] (B) to (tau2);
            \draw [style=inarrow] (tau2) to (AB);
            \draw [style=inarrow] (AA) to (tau3);
            \draw [style=inarrow] (AB) to (tau3);
            \draw [style=inarrow, bend left=30] (C) to (tau3);
            \draw [style=inarrow] (tau3) to (AAAB);
            \draw [style=inarrow, bend left=30] (tau3) to (C);
            \draw [style=inarrow] (AAAB) to (tau4);
            \draw [style=inarrow, bend right=30] (tau4) to (A);
            \draw [style=inarrow, bend right=30] (tau4) to (AA);
            \draw [style=inarrow, bend left=40] (tau4) to (B);
        \end{pgfonlayer}
    \end{tikzpicture}
}
\end{figure}

>>>>

\tikzstyle{empty}=[circle,fill=none, draw=none]
\tikzstyle{inputdot}=[circle,fill=black,draw=black, scale=.5]
\tikzstyle{dot}=[circle,fill=black,draw=black]
\tikzstyle{bounding}=[circle,dashed, fill=none,draw=black, scale=9.00]
\tikzstyle{simple}=[-,draw=black,line width=1.000]
\tikzstyle{arrow}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.000]
\tikzstyle{tick}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\draw (0,-0.1) -- (0,0.1);}},line width=1.000]
\tikzstyle{inputarrow}=[->,draw=black, shorten >=.05cm]
\tikzstyle{sitemap}=[->, dashed, draw=red, ultra thick, shorten >=.05cm]
\tikzstyle{transitionmap}=[->, dashed, draw=blue, ultra thick, shorten >=.05cm]

@@

We wish to represent the idea of assembling objects out of ``simpler'' objects, in some sense of the word.
To formalize this idea, we will build off of the concept of a \textit{Petri net}.
In simple terms, a Petri net is a set of sites which we think of as representing types of objects, e.g. molecules, building materials, characters, etc..., and a set of transitions representing the ways in which sites can be combined to yield other sites.
For the sake of formalism, we somewhat elevate the transitions above the sites in that we mostly consider the ``inputs'' and ``outputs'' of transitions, rather the transitions that a given site participates in.
With this in mind, we formally define a Petri net as follows.

@@

The maps $\sigma$ and $\tau$ assign to each transition a formal linear combination of sites.
Picking up our molecular example from the previous section, we can consider the Petri net with sites $S = \{\ce{H_2}, \ce{O_2}, \ce{H_2O}\}$, a single transition $T = \{\alpha\}$, and source and target maps
\begin{equation*}
    \begin{tikzcd}
        \alpha \arrow[r, mapsto, "\sigma"] & 2\ce{H_2} + \ce{O_2}
        \quad\textrm{and}\quad
        \alpha \arrow[r, mapsto, "\tau"] & 2\ce{H_2O}
    \end{tikzcd}
\end{equation*}

There is a natural way of graphically representing a Petri net as a bipartite multigraph:

\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site] (H2) at (0, 1) {$\ce{H_2}$};
                \node [style=site] (O2) at (0, -1) {$\ce{O_2}$};
                \node [style=site] (H2O) at (4, 0) {$\ce{H_2O}$};
                \node [style=transition] (alpha) at (2, 0) {$\alpha$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, bend right=15] (H2) to (alpha);
                \draw [style=arrow, bend left=15] (H2) to (alpha);
                \draw [style=arrow] (O2) to (alpha);
                \draw [style=arrow, bend right=15] (alpha) to (H2O);
                \draw [style=arrow, bend left=15] (alpha) to (H2O);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}

We read this as ``\textit{transition $\alpha$ can only proceed if at least two $\ce{H_2}$ and one $\ce{O_2}$ are present in the system, and will yield two $\ce{H_2O}$ when it does}''.
In essence, this is a statement about was can possibly happen, not necessarily what will happen; that's more a question of dynamics.

As a more elaborate example, one which we will repeatedly refer to as we expand on the formalism, we imagine a simple ligation type process where in the characters $A$ and $B$ can be combined into strings and $C$ acts something like a \red{``catalyst''} making some transitions possible if and only if $C$ exists.
Consider the Petri $P$ net described by $S(P) = \{ A, B, C, AA, AB, AAAB \}$ and $T(P) = \{ \alpha, \beta, \gamma, \delta \}$ with source and target maps:

\begin{align*}
    \sigma(\alpha) &= 2A           & \tau(\alpha) &= AA         \\
    \sigma(\beta)  &= A + B        & \tau(\beta)  &= AB         \\
    \sigma(\gamma) &= AA + AB + C  & \tau(\gamma) &= AAAB + C   \\
    \sigma(\delta) &= AAAB         & \tau(\delta) &= A + AA + B
\end{align*}

which we graphically represent as

\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site] (A) at (0, 0.8) {$A$};
                \node [style=site] (B) at (0, -0.8) {$B$};
                \node [style=site] (C) at (6, -1.6) {$C$};
                \node [style=site] (AA) at (4, 0.8) {$AA$};
                \node [style=site] (AB) at (4, -0.8) {$AB$};
                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
                \node [style=transition] (tau4) at (10, 0) {$\delta$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, bend right=15] (A) to (tau1);
                \draw [style=arrow, bend left=15] (A) to (tau1);
                \draw [style=arrow, bend right=15] (A) to (tau2);
                \draw [style=arrow] (tau1) to (AA);
                \draw [style=arrow] (B) to (tau2);
                \draw [style=arrow] (tau2) to (AB);
                \draw [style=arrow] (AA) to (tau3);
                \draw [style=arrow] (AB) to (tau3);
                \draw [style=arrow, bend left=30] (C) to (tau3);
                \draw [style=arrow] (tau3) to (AAAB);
                \draw [style=arrow, bend left=30] (tau3) to (C);
                \draw [style=arrow] (AAAB) to (tau4);
                \draw [style=arrow, bend right=30] (tau4) to (A);
                \draw [style=arrow, bend right=30] (tau4) to (AA);
                \draw [style=arrow, bend left=40] (tau4) to (B);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}

This particular example exhibits a number of interesting features.
First, there are transitions wherein one of the input sites is also an output site, namely $\gamma$'s dependence on $C$.
Drawing from chemical parlance, this represents a catalytic effect; the transition can only proceed when the site is present\footnote{The addition of another transitition next to $\gamma$ which does not depend on or yield $C$ can model processes that can proceed without $C$ but is accelerated by it.}.
Second, transitions such as $\delta$ can be viewed as a degradation or disassembly process.
This allows reactions to run in both directions.
To elaborate on this point, we can return to the water example and introduce a second transition allowing for the degradation of water back into Hydrogen and Oxygen:

\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site] (H2) at (0, 1) {$\ce{H_2}$};
                \node [style=site] (O2) at (0, -1) {$\ce{O_2}$};
                \node [style=site] (H2O) at (4, 0) {$\ce{H_2O}$};
                \node [style=transition] (alpha) at (2, 0) {$\alpha$};
                \node [style=transition] (beta) at (6, 0) {$\beta$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, bend right=15] (H2) to (alpha);
                \draw [style=arrow, bend left=15] (H2) to (alpha);
                \draw [style=arrow] (O2) to (alpha);
                \draw [style=arrow, bend right=15] (alpha) to (H2O);
                \draw [style=arrow, bend left=15] (alpha) to (H2O);
                \draw [style=arrow, bend right=15] (H2O) to (beta);
                \draw [style=arrow, bend left=15] (H2O) to (beta);
                \draw [style=arrow, bend right=25] (beta.north) to (H2);
                \draw [style=arrow, bend right=15] (beta.north) to (H2);
                \draw [style=arrow, bend left=15] (beta.south) to (O2);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}

@@

\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site] (A) at (0, 0.8) {$A$};
                \node [style=site] (B) at (0, -0.8) {$B$};
                \node [style=site] (C) at (6, -1.6) {$C$};
                \node [style=site] (AA) at (4, 0.8) {$AA$};
                \node [style=site] (AB) at (4, -0.8) {$AB$};
                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
                \node [style=transition] (tau3) at (6, 0) {$\gamma$};
                \node [style=transition] (tau4) at (10, 0) {$\delta$};

@@

                \node [text=red, scale=2] (g) at (-1.5, -3) {$g$};
                \node [text=blue, scale=2] (f) at (0.5, -3) {$f$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau1);
                \draw [style=arrow, draw=gray!80, bend left=15] (A) to (tau1);
                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau2);
                \draw [style=arrow, draw=gray!80] (tau1) to (AA);
                \draw [style=arrow, draw=gray!80] (B) to (tau2);
                \draw [style=arrow, draw=gray!80] (tau2) to (AB);
                \draw [style=arrow, draw=gray!80] (AA) to (tau3);
                \draw [style=arrow, draw=gray!80] (AB) to (tau3);
                \draw [style=arrow, draw=gray!80, bend left=30] (C) to (tau3);
                \draw [style=arrow, draw=gray!80] (tau3) to (AAAB);
                \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);
                \draw [style=arrow, draw=gray!80] (AAAB) to (tau4);
                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (A);
                \draw [style=arrow, draw=gray!80, bend right=30] (tau4) to (AA);
                \draw [style=arrow, draw=gray!80, bend left=40] (tau4) to (B);

                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
                \draw [style=arrow, draw=gray!80, bend left=15] (X) to (tau6);
                \draw [style=arrow, draw=gray!80, bend right=15] (X) to (tau6);
                \draw [style=arrow, draw=gray!80] (tau6) to (Y);
                \draw [style=arrow, draw=gray!80, bend left=20] (Y) to (tau7);
                \draw [style=arrow, draw=gray!80] (Y) to (tau7);
                \draw [style=arrow, draw=gray!80, bend right=20] (Y) to (tau7);
                \draw [style=arrow, draw=gray!80] (tau7) to (Z);
                \draw [style=arrow, draw=gray!80, bend left=50] (tau7.south) to (Y.south);
                \draw [style=arrow, draw=gray!80] (Z) to (tau8);
                \draw [style=arrow, draw=gray!80, bend left=30] (tau8) to (X);
                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (X);
                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (Y);

                \draw [style=sitemap, bend right=30] (A) to (X);
                \draw [style=sitemap, bend right=30] (B) to (X);
                \draw [style=sitemap, bend right=30] (AA) to (Y);
                \draw [style=sitemap, bend right=30] (AB) to (Y);
                \draw [style=sitemap, bend right=30] (C) to (Y);
                \draw [style=sitemap, bend right=30] (AAAB) to (Z);
                \draw [style=transitionmap, bend right=30] (tau1) to (tau6);
                \draw [style=transitionmap, bend right=30] (tau2) to (tau6);
                \draw [style=transitionmap, bend right=30] (tau3) to (tau7);
                \draw [style=transitionmap, bend right=30] (tau4) to (tau8);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}

@@

\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site] (A) at (0, 0.8) {$A$};
                \node [style=site] (B) at (0, -0.8) {$B$};
                \node [style=site] (C) at (6, -1.6) {$C$};
                \node [style=site] (AA) at (4, 0.8) {$AA$};
                \node [style=site] (AB) at (4, -0.8) {$AB$};
                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
                \node [style=transition] (tau1) at (2, 0.8) {$\alpha$};
                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
                \node [style=transition] (tau3) at (6, 0) {$\gamma$};

                \node [style=site] (W) at (-4, -6) {$W$};
                \node [style=site, fill=green!20] (X) at (0, -6) {$X$};
                \node [style=site, fill=green!20] (Y) at (4, -6) {$Y$};
                \node [style=site, fill=green!20] (Z) at (8, -6) {$Z$};
                \node [style=transition] (tau5) at (-2, -6) {$\phi$};
                \node [style=transition, fill=yellow!20] (tau6) at (2, -6) {$\chi$};
                \node [style=transition, fill=yellow!20] (tau7) at (6, -6) {$\psi$};
                \node [style=transition] (tau8) at (10, -6) {$\omega$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau1);
                \draw [style=arrow, draw=gray!80, bend left=15] (A) to (tau1);
                \draw [style=arrow, draw=gray!80, bend right=15] (A) to (tau2);
                \draw [style=arrow, draw=gray!80] (tau1) to (AA);
                \draw [style=arrow, draw=gray!80] (B) to (tau2);
                \draw [style=arrow, draw=gray!80] (tau2) to (AB);
                \draw [style=arrow, draw=gray!80] (AA) to (tau3);
                \draw [style=arrow, draw=gray!80] (AB) to (tau3);
                \draw [style=arrow, draw=gray!80, bend left=30] (C) to (tau3);
                \draw [style=arrow, draw=gray!80] (tau3) to (AAAB);
                \draw [style=arrow, draw=gray!80, bend left=30] (tau3) to (C);

                \draw [style=arrow, draw=gray!80, bend left=15] (W) to (tau5);
                \draw [style=arrow, draw=gray!80, bend right=15] (W) to (tau5);
                \draw [style=arrow, draw=gray!80, bend left=15] (tau5) to (X);
                \draw [style=arrow, draw=gray!80, bend right=15] (tau5) to (X);
                \draw [style=arrow, draw=red, bend left=15] (X) to (tau6);
                \draw [style=arrow, draw=red, bend right=15] (X) to (tau6);
                \draw [style=arrow, draw=red] (tau6) to (Y);
                \draw [style=arrow, draw=red, bend left=20] (Y) to (tau7);
                \draw [style=arrow, draw=red] (Y) to (tau7);
                \draw [style=arrow, draw=red, bend right=20] (Y) to (tau7);
                \draw [style=arrow, draw=red] (tau7) to (Z);
                \draw [style=arrow, draw=red, bend left=50] (tau7.south) to (Y.south);
                \draw [style=arrow, draw=gray!80] (Z) to (tau8);
                \draw [style=arrow, draw=gray!80, bend left=30] (tau8) to (X);
                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (X);
                \draw [style=arrow, draw=gray!80, bend right=30] (tau8) to (Y);

                \draw [style=sitemap, bend right=30, shorten >=2mm] (A) to (X);
                \draw [style=sitemap, bend right=30, shorten >=2mm] (B) to (X);
                \draw [style=sitemap, bend right=30, shorten >=2mm] (AA) to (Y);
                \draw [style=sitemap, bend right=30, shorten >=2mm] (AB) to (Y);
                \draw [style=sitemap, bend right=30, shorten >=2mm] (C) to (Y);
                \draw [style=sitemap, bend right=30, shorten >=2mm] (AAAB) to (Z);
                \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau1) to (tau6);
                \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau2) to (tau6);
                \draw [style=transitionmap, bend right=30, shorten >=2mm] (tau3) to (tau7);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}

@@

\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site] (A) at (2, 0.8) {$A$};
                \node [style=site] (B) at (2, -0.8) {$B$};
                \node [style=transition] (tau1) at (0, 0) {$\alpha$};
                \node [style=transition] (tau2) at (4, 0) {$\beta$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, bend left=15] (tau1) to (A);
                \draw [style=arrow, bend right=15] (tau1) to (B);
                \draw [style=arrow, bend left=15] (A) to (tau2);
                \draw [style=arrow, bend right=15] (B) to (tau2);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}

@@

\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site] (A) at (0, 0.8) {$A$};
                \node [style=site] (B) at (0, -0.8) {$B$};
                \node [style=site] (C) at (6, -1.6) {$C$};
                \node [style=site] (AA) at (4, 0.8) {$AA$};
                \node [style=site] (AB) at (4, -0.8) {$AB$};
                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
                \node [style=transition, fill=green!20] (tau1) at (2, 0.8) {$\alpha$};
                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
                \node [style=transition, fill=green!20] (tau3) at (6, 0) {$\gamma$};
                \node [style=transition] (tau4) at (10, 0) {$\delta$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, bend right=15] (A) to (tau1);
                \draw [style=arrow, bend left=15] (A) to (tau1);
                \draw [style=arrow, bend right=15] (A) to (tau2);
                \draw [style=arrow] (tau1) to (AA);
                \draw [style=arrow] (B) to (tau2);
                \draw [style=arrow] (tau2) to (AB);
                \draw [style=arrow] (AA) to (tau3);
                \draw [style=arrow] (AB) to (tau3);
                \draw [style=arrow, bend left=30] (C) to (tau3);
                \draw [style=arrow] (tau3) to (AAAB);
                \draw [style=arrow, bend left=30] (tau3) to (C);
                \draw [style=arrow] (AAAB) to (tau4);
                \draw [style=arrow, bend right=30] (tau4) to (A);
                \draw [style=arrow, bend right=30] (tau4) to (AA);
                \draw [style=arrow, bend left=40] (tau4) to (B);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}
